Article - Figures

### 2020-12-21 article_figures_FLORIAN_RICOUR.Rmd
update markdown for figs

#REPLACE FLUO WITH SMOOTHED FLUO & CDOM
data[,3] <- smoothed_fluo
data[,4] <- smoothed_cdom
data <- clean_remove(data, unique(data$juld))
data_info <- ddply(data,~juld,summarize,
                    qc_fluo = qc_fluo[which.max(fluo)],
                    depthmax = depth[which.max(fluo)],
                    maxvalue = fluo[which.max(fluo)],
                    depthmin = depth[which.max(fluo):length(fluo)][which.min(fluo[which.max(fluo):length(fluo)])],
                    integration = sum(fluo),
                    bottomdepth = max(depth),
                    min_depth = min(depth),
                    dir = dir[1],
                    lon=mean(lon),
                    lat=mean(lat),
                    platform = platform[1],
                    day = day[1], month = month[1],
                    year = year[1], DOY = DOY[1])
rm(ncfile, smoothed_cdom, smoothed_fluo)
```

@@

```{r correction_fig, include = T}
#HPLC DATA FROM DEPLOYMENT
depth_hplc <- c(0,30,50,70,90,100,140,200,250,500,750,1000)
chla_hplc <- c(0.6111,0.6433,0.3090,0.0675,0.0229,0.0168,0.012,0.0032,
               0.0035, 0.0023, 0.0039, 0.0042)
hplc <- as.data.frame(cbind(depth_hplc, chla_hplc))

@@

deployment <- ggplot(data, aes(x = fluo, y = depth, colour = "ROESLER + FDOM + NPQ"), lwd = 1.5) + geom_path(lwd = 1.5) +
  scale_y_reverse() + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM"), lwd = 1.5) +
  xlab(expression(Chlorophyll~a~(mg/m^3)))+ ylab("Depth [m]") +
  geom_hline(yintercept = data_info$depthmin[1], color = "black", lty = 2) +
  annotate("text", x = .8, y = data_info$depthmin[1]-20, label = "CHLA MINIMUM") +
  geom_path(data = data, aes(x = raw_fluo, y = depth, colour = "None"), lwd = 1.5) + 
  geom_path(data = data, aes(x = raw_roesler, y = depth, colour = "ROESLER"), lwd = 1.5) + 
  geom_point(data = df, aes(x = cdom/10, y = depth), colour = "black", size = .5) + 
  geom_point(data=hplc, aes(y = depth_hplc, x = chla_hplc), colour = "red", size = 2, shape = 15)  + 
  scale_color_discrete(name = "Correction") +
  theme_bw() + theme(legend.position = "none")

@@

```{r shapes, include = T}
fit_curve <- function(i){
  tmp <- init_fit[i,]
  juld <- tmp$juld
  tmp2 <- init_profiles[init_profiles$juld == juld,]
  shape <- as.character(tmp$shape)
  tmp2$fluo <- normalize(tmp2$fluo) #
  depthindex <- which.min(tmp2$depth <= 90)
  tmp2 <- tmp2[1:depthindex,]
  tab <- data.frame(x=tmp2$depth,y=tmp2$fluo)
  z <- tab$x
  # only 4 shapes (E has not been encountered)
  if(shape == "G"){
    dat <- as.data.frame(fgauss(z, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "S"){
    dat <- as.data.frame(fsigmoid(z, tmp$Fsurf, tmp$Zdemi, tmp$s))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "GS"){
    dat <- as.data.frame(fgauss_sigmoid(z, tmp$Fsurf, tmp$Zdemi, tmp$s, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "GE"){
    dat <- as.data.frame(fgauss_expo(z, tmp$Fsurf, tmp$Zdemi, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }
  ggplot(tmp2, aes(x = fluo, y = depth)) + geom_point() + scale_y_reverse(limits = c(90,0)) +
    xlab("Normalized Chla") + ylab("Depth [m]") + geom_path(data = dat, aes(x = fit, y = tmp2$depth), colour = "red") +
    #theme(text=element_text(size=12)) 
    theme_bw()

}
```

```{r profile_examples}

flabels <- c("Gaussian (G)","Sigmoid (S)","Gaussian-Sigmoid (GS)","Gaussian-Exponential (GE)")
profID  <- c(111,7,12,195)

ex1 <- fit_curve(profID[1])+ggtitle(flabels[1]) + theme(axis.title.x=element_blank())
ex2 <- fit_curve(profID[2])+ggtitle(flabels[2]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank())
ex3 <- fit_curve(profID[3])+ggtitle(flabels[3]) 
ex4 <- fit_curve(profID[4])+ggtitle(flabels[4]) + theme(axis.title.y=element_blank())

grid.arrange(ex1, ex2, ex3, ex4, nrow = 2, ncol = 2)

>>>>

#REPLACE FLUO WITH SMOOTHED FLUO & CDOM
data[,3] <- smoothed_fluo
data[,4] <- smoothed_cdom
data <- clean_remove(data, unique(data$juld))
data_info <- ddply(data,~juld,summarize,
                    qc_fluo = qc_fluo[which.max(fluo)],
                    depthmax = depth[which.max(fluo)],
                    maxvalue = fluo[which.max(fluo)],
                    depthmin = depth[which.max(fluo):length(fluo)][which.min(fluo[which.max(fluo):length(fluo)])],
                    integration = sum(fluo),
                    bottomdepth = max(depth),
                    min_depth = min(depth),
                    dir = dir[1],
                    lon=mean(lon),
                    lat=mean(lat),
                    platform = platform[1],
                    day = day[1], month = month[1],
                    year = year[1], DOY = DOY[1])

rm(ncfile, smoothed_cdom, smoothed_fluo)
```

@@

```{r correction_fig, include = T, fig.width=8}
#HPLC DATA FROM DEPLOYMENT
depth_hplc <- c(0,30,50,70,90,100,140,200,250,500,750,1000)
chla_hplc <- c(0.6111,0.6433,0.3090,0.0675,0.0229,0.0168,0.012,0.0032,
               0.0035, 0.0023, 0.0039, 0.0042)
hplc <- as.data.frame(cbind(depth_hplc, chla_hplc))

@@

deployment <- ggplot(data, aes(x = fluo, y = depth, colour = "ROESLER + FDOM + NPQ"), lwd = 1.5) + geom_path(lwd = 1.5) +
  scale_y_reverse() + geom_path(data = data, aes(x = raw_roesler_fdom, y = depth, colour = "ROESLER + FDOM"), lwd = 1.5) +
  #xlab(expression(Chlorophyll~a~(mg/m^3)))+ 
  ylab("Depth [m]") +
  geom_hline(yintercept = data_info$depthmin[1], color = "black", lty = 2) +
  annotate("text", x = .8, y = data_info$depthmin[1]-20, label = "CHLA MINIMUM") +
  geom_path(data = data, aes(x = raw_fluo, y = depth, colour = "None"), lwd = 1.5) + 
  geom_path(data = data, aes(x = raw_roesler, y = depth, colour = "ROESLER"), lwd = 1.5) + 
  geom_point(data = df, aes(x = cdom/10, y = depth), colour = "black", size = .5) + 
  geom_point(data=hplc, aes(y = depth_hplc, x = chla_hplc), colour = "red", size = 2, shape = 15)  + 
  scale_color_discrete(name = "Correction") +
  theme_bw() + theme(legend.position = "none") +
  # add a secondary axis
  scale_x_continuous(expression(Chlorophyll~a~(mg/m^3)), sec.axis = dup_axis(name = "CDOM (ppb)", trans = ~ .*10))

@@

```{r shapes, include = T}
fit_curve <- function(i){
  tmp <- init_fit[i,]
  juld <- tmp$juld
  tmp2 <- init_profiles[init_profiles$juld == juld,]
  shape <- as.character(tmp$shape)
  tmp2$fluo <- normalize(tmp2$fluo) #
  depthindex <- which.min(tmp2$depth <= 90)
  tmp2 <- tmp2[1:depthindex,]
  tab <- data.frame(x=tmp2$depth,y=tmp2$fluo)
  z <- tab$x
  # only 4 shapes (E has not been encountered)
  if(shape == "G"){
    dat <- as.data.frame(fgauss(z, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "S"){
    dat <- as.data.frame(fsigmoid(z, tmp$Fsurf, tmp$Zdemi, tmp$s))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "GS"){
    dat <- as.data.frame(fgauss_sigmoid(z, tmp$Fsurf, tmp$Zdemi, tmp$s, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "GE"){
    dat <- as.data.frame(fgauss_expo(z, tmp$Fsurf, tmp$Zdemi, tmp$Fmax, tmp$Zmax, tmp$dz))
    colnames(dat) <- "fit"
    dat$fit <- normalize(dat$fit)
    dat <- cbind(tmp2$depth, dat)
  }else if(shape == "O"){
    return(ggplot(tmp2, aes(x = fluo, y = depth)) + geom_point() + scale_y_reverse(limits = c(90,0)) +
    xlab("Normalized Chla") + ylab("Depth [m]") + theme_bw())
  }
  ggplot(tmp2, aes(x = fluo, y = depth)) + geom_point() + scale_y_reverse(limits = c(90,0)) +
    xlab("Normalized Chla") + ylab("Depth [m]") + geom_path(data = dat, aes(x = fit, y = tmp2$depth), colour = "red") +
    #theme(text=element_text(size=12)) 
    theme_bw()
}
```

```{r profile_examples, fig.height=10, fig.width=10}

flabels <- c("Gaussian (G)","Sigmoid (S)","Gaussian-Sigmoid (GS)","Gaussian-Exponential (GE)", "NON-DCM GS",
             "NON-DCM GE", "Other (O)", "NON-DCM G")
profID  <- c(111,7,12,195,3,222,656,143)

# DCM
ex1 <- fit_curve(profID[1])+ggtitle(flabels[1]) + theme(axis.title.x=element_blank()) # DCM - Gaussian
ex2 <- fit_curve(profID[2])+ggtitle(flabels[2])  # NON-DCM - Sigmoid
ex3 <- fit_curve(profID[3])+ggtitle(flabels[3]) + theme(axis.title.x=element_blank()) # DCM - GS
ex4 <- fit_curve(profID[4])+ggtitle(flabels[4]) + theme(axis.title.x=element_blank()) # GE

# NON DCM : O, GE, G, GS
ex5 <- fit_curve(profID[5])+ggtitle(flabels[5]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank()) # NON-DCM - GS
ex6 <- fit_curve(profID[6])+ggtitle(flabels[6]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank()) # GE
ex7 <- fit_curve(profID[7])+ggtitle(flabels[7]) + theme(axis.title.y=element_blank()) # O
ex8 <- fit_curve(profID[8])+ggtitle(flabels[8]) + theme(axis.title.y=element_blank()) + theme(axis.title.x=element_blank()) # G

grid.arrange(ex1, ex8, ex3, ex5, ex4, ex6, ex2, ex7, nrow = 4, ncol = 2)
